Same as always: I suck at titles

### 2024-09-13 manuscript/manuscript_eb.Rmd
edits manuscripts

abstract: |
  Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the situational (e.g, who is speaking) to the ephemeral (e.g., how they speak). Listeners are more likely to evaluate non-native speakers as less veracious, more deceiving, and evaluate the speaker as less competent. Similar judgements are elicited by how fluent speech is: Filled pauses, such as _uh_ or _um_ in English, elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge. Interestingly, the co-existence of these two cues has been shown to yield, sometimes, different processes. However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear. In a horse-race betting paradigm, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge. This suggests that previous reported perceptions of knowledgeability elicited explicitly have an impact on how individuals use the information they are given, even in situations when it is not advantageous. Although there is evidence for pragmatic leniance towards non-native speakers, it may be the case that this only applies to failures in language skills that are believed to require high proficiency (e.g., irony), whilst hesitation phenomena may not be subject to such forgiveness. Overall, our results align with a broader body of literature suggesting that the interpretation of hesitation phenomena is not context-dependent.

@@

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

@@

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confident a speaker is perceived [@jiangetal2019; @caballeropell2020]. Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and is perceived as such by native listenes [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014].

@@

## Results

@@

```{r include=FALSE}
source('../analysis/data-visualization.R')
```
```{r tab-dist-money}
apa_table(
  tab4,
  caption = "Mean (standard deviation) of money bet by manner of delivery and speaker’s linguistic
background."
)
```
```{r fig1, out.width="90%",fig.align='center', fig.cap="Money distribution by manner of delivery (fluent/disfluent) and speaker (green: native/orange: non-native)."}
fig1
```

@@

@@

@@

>>>>

abstract: |
  Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the ephemeral (e.g., how speech is produced) to the situational (e.g., who is speaking). The presence of disfluencies, such as filled pauses (e.g., _uh_ or _um_ in English), elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge. On the other hand, listeners consider alternative explanations for the speaker to be underinformative: Specifically, non-native speakers are more likely to be forgiven when they fail to be informative. However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear. In a horse-race betting paradigm, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge. This suggests that previous reported perceptions of knowledgeability elicited explicitly have an impact on how individuals use the information they are given, even in situations when it is not advantageous. Although there is evidence for pragmatic leniance towards non-native speakers, it may be the case that this only applies to failures in language skills that are believed to require high proficiency (e.g., irony), whilst hesitation phenomena may not be subject to such forgiveness. Overall, our results align with a broader body of literature suggesting that the interpretation of hesitation phenomena is not context-dependent.

@@

figurelist        : yes
tablelist         : yes
footnotelist      : no

classoption       : "man"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---

@@

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confident a speaker is perceived [@jiangetal2019; @caballeropell2020]. Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and is perceived as such by native listenes [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.

@@

# Results

@@

```{r include=FALSE}
source('../analysis/data-visualization.R')
```

@@

```{r tab-dist-money}
apa_table(
  tab4,
  caption = "Mean (standard deviation) of money bet by manner of delivery and speaker’s linguistic
background."
)
```

```{r fig1, out.width="90%",fig.align='center', fig.cap="Money distribution by manner of delivery (fluent/disfluent) and speaker (green: native/orange: non-native)."}
fig1
```

@@

Listeners can infer speaker's knowledgeability from a range of cues, such as voice pitch or amplitude. A speaker's speech fluency i.e., whether they produces disfluencies as they speak, has been previously shown to impact how confident in their knowledge a speaker is judged to be [@brennanwilliams1995]. However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in own's second language is also associated with an increase in disfluencies [@dejongetal2015;@derwingetal2009]. In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance [@levari2015], which consequently leads native listeners to "forgive" what otherwise would be lead to a negative evaluation [@lorenzonietal2022; @fairchildetal2020]. In the present experiment, we explored whether attributions of (un)knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse. Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.

@@

This inference explanation would predict that listeners would forgive foreign disfluencies, in line with the expectations-based account. While previous research has reported that whether a filled pause affects processes involved in speech comprehension depending on speaker identity [e.g., @boskeretal2014], recent studies have failed to find this effect when it comes to speaker's attributions [@matzingeretal2023]. In our experiment, participants distributed money similarly when either speaker provided disfluent descriptions, suggesting that listeners did not weigh in our (non-native) speaker's identity to interpret the disfluency. This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.  One possibility for this lack of interaction has to do with the fact that our non-native speaker was introduced as a knowledgeable tipster. This introduction of the speaker as an authoritative figure may have overridden any other features of their identity, including their non-native speaker identity. Indeed, beliefs about a speaker's expertise have been shown to guide perceptions of their certainty [@moletal2013]. Considering the language attitudes triggered by both accents, the difference in speaker preference may more likely reflect the ease of comprehending the native speaker, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of competence for non-native speakers.

The experiment here also introduced a novel approach to measuring how certain the speaker is perceived. While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study offers a new venue to explore how different factors bias individuals' evaluations indirectly, as well as the implications of those evaluations. However, a potential shortcoming of our design has to do with how people approached the betting system. Because of the nature of the task, in that we tested participants with no prior knowledge of horse races, our participants behaved rationally: The vast majority employed the hundred pounds allocated and distributed them fairly rationally in a way that maximizes their chances of winning (i.e., around £25 per horse). It is, therefore, possible that in situations of less uncertainty (e.g., a scenario where individuals have more knowledge) or where they are rewarded for allocating money to the winning horse, how the speaker is perceived may yield a larger effect on participants' behaviours.

### 2024-09-13 manuscript/manuscript_eb.tex
edits manuscripts

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Same as always: I suck at titles},
  pdfauthor={Esperanza Badaya1, Robert J. Hartsuiker1, \& Martin Corley2},
  pdflang={en-EN},
  pdfkeywords={filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the situational (e.g, who is speaking) to the ephemeral (e.g., how they speak). Listeners are more likely to evaluate non-native speakers as less veracious, more deceiving, and evaluate the speaker as less competent. Similar judgements are elicited by how fluent speech is: Filled pauses, such as \emph{uh} or \emph{um} in English, elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge. Interestingly, the co-existence of these two cues has been shown to yield, sometimes, different processes. However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear. In a horse-race betting paradigm, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge. This suggests that previous reported perceptions of knowledgeability elicited explicitly have an impact on how individuals use the information they are given, even in situations when it is not advantageous. Although there is evidence for pragmatic leniance towards non-native speakers, it may be the case that this only applies to failures in language skills that are believed to require high proficiency (e.g., irony), whilst hesitation phenomena may not be subject to such forgiveness. Overall, our results align with a broader body of literature suggesting that the interpretation of hesitation phenomena is not context-dependent.
}

@@

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confident a speaker is perceived (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019). Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and is perceived as such by native listenes (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014).

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

\end{table}
\begin{figure}[H]

@@

@@

@@

@@

@@

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\cftpagenumbersoff{table}
\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
\renewcommand{\cfttabaftersnum}{.\space}
\setlength{\cfttabindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cfttabnumwidth}{Table 10.\qquad}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Same as always: I suck at titles},
  pdfauthor={Esperanza Badaya1, Robert J. Hartsuiker1, \& Martin Corley2},
  pdflang={en-EN},
  pdfkeywords={filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the ephemeral (e.g., how speech is produced) to the situational (e.g., who is speaking). The presence of disfluencies, such as filled pauses (e.g., \emph{uh} or \emph{um} in English), elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge. On the other hand, listeners consider alternative explanations for the speaker to be underinformative: Specifically, non-native speakers are more likely to be forgiven when they fail to be informative. However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear. In a horse-race betting paradigm, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge. This suggests that previous reported perceptions of knowledgeability elicited explicitly have an impact on how individuals use the information they are given, even in situations when it is not advantageous. Although there is evidence for pragmatic leniance towards non-native speakers, it may be the case that this only applies to failures in language skills that are believed to require high proficiency (e.g., irony), whilst hesitation phenomena may not be subject to such forgiveness. Overall, our results align with a broader body of literature suggesting that the interpretation of hesitation phenomena is not context-dependent.
}

@@

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confident a speaker is perceived (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019). Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and is perceived as such by native listenes (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\begin{figure}[H]

@@

Listeners can infer speaker's knowledgeability from a range of cues, such as voice pitch or amplitude. A speaker's speech fluency i.e., whether they produces disfluencies as they speak, has been previously shown to impact how confident in their knowledge a speaker is judged to be (Brennan \& Williams, 1995). However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in own's second language is also associated with an increase in disfluencies (De Jong, Groenhout, Schoonen, \& Hulstijn, 2015; Derwing, Munro, Thomson, \& Rossiter, 2009). In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance (Lev-Ari, 2015), which consequently leads native listeners to ``forgive'' what otherwise would be lead to a negative evaluation (Fairchild et al., 2020; Lorenzoni et al., 2022). In the present experiment, we explored whether attributions of (un)knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse. Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.

@@

This inference explanation would predict that listeners would forgive foreign disfluencies, in line with the expectations-based account. While previous research has reported that whether a filled pause affects processes involved in speech comprehension depending on speaker identity (e.g., Bosker, Quené, Sanders, \& De Jong, 2014), recent studies have failed to find this effect when it comes to speaker's attributions (Matzinger et al., 2023). In our experiment, participants distributed money similarly when either speaker provided disfluent descriptions, suggesting that listeners did not weigh in our (non-native) speaker's identity to interpret the disfluency. This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future. One possibility for this lack of interaction has to do with the fact that our non-native speaker was introduced as a knowledgeable tipster. This introduction of the speaker as an authoritative figure may have overridden any other features of their identity, including their non-native speaker identity. Indeed, beliefs about a speaker's expertise have been shown to guide perceptions of their certainty (Mol, Kuhlen, Van der Steen, \& Obbens, 2013). Considering the language attitudes triggered by both accents, the difference in speaker preference may more likely reflect the ease of comprehending the native speaker, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of competence for non-native speakers.

The experiment here also introduced a novel approach to measuring how certain the speaker is perceived. While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study offers a new venue to explore how different factors bias individuals' evaluations indirectly, as well as the implications of those evaluations. However, a potential shortcoming of our design has to do with how people approached the betting system. Because of the nature of the task, in that we tested participants with no prior knowledge of horse races, our participants behaved rationally: The vast majority employed the hundred pounds allocated and distributed them fairly rationally in a way that maximizes their chances of winning (i.e., around £25 per horse). It is, therefore, possible that in situations of less uncertainty (e.g., a scenario where individuals have more knowledge) or where they are rewarded for allocating money to the winning horse, how the speaker is perceived may yield a larger effect on participants' behaviours.

@@

\leavevmode\vadjust pre{\hypertarget{ref-dejongetal2015}{}}%
De Jong, N. H., Groenhout, R., Schoonen, R., \& Hulstijn, J. H. (2015). Second language fluency: Speaking style or proficiency? Correcting measures of second language fluency for first language behavior. \emph{Applied Psycholinguistics}, \emph{36}(2), 223--243.

@@

\leavevmode\vadjust pre{\hypertarget{ref-derwingetal2009}{}}%
Derwing, T. M., Munro, M. J., Thomson, R. I., \& Rossiter, M. J. (2009). The relationship between L1 fluency and L2 fluency development. \emph{Studies in Second Language Acquisition}, \emph{31}(4), 533--557.

@@

\leavevmode\vadjust pre{\hypertarget{ref-moletal2013}{}}%
Mol, L., Kuhlen, A., Van der Steen, R., \& Obbens, M. (2013). Beliefs about a speaker affect feeling of another's knowing. \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{35}.

@@

\clearpage
\renewcommand{\listfigurename}{Figure captions}

\clearpage
\renewcommand{\listtablename}{Table captions}
